Calendar-based graphics for visualizing people's daily schedules

### 2019-03-14 main.Rmd
used bookdown::pdf_book

bibliography: bibliography.bib
output: 
  rticles::asa_article:
    base_format: bookdown::pdf_document2
---

@@

```{r h4, fig.height = 7, fig.cap = "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, April, and June."}
```

>>>>

bibliography: bibliography.bib
output: 
  bookdown::pdf_book:
    base_format: rticles::asa_article
---

@@

```{r h4, fig.height = 7, fig.cap = "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Four short trips were taken in October, December, April, and June."}
```
